Automatically Splitting a Staged Lambda Calculus

### 2015-07-10 paper/overview.tex
Made a few tiny edits while reading.

\begin{theorem*}
  Consider an execution of \texttt{qs1} with a randomly permuted input
  of $n$ keys and performing $m$ executions of \texttt{qs2} with the
  result of \texttt{qs1}.  The total run-time for this computation is
  $\Theta(n\log{n} + m\log{n})$ in expectation.
\end{theorem*}
\begin{proof}
  We use a few standard facts.  We note first that \texttt{qs1} is
  isomorphic to a quicksort algorithm but builds a binary search tree
  instead of combining the returned results in a list.  The run-time
  for \texttt{qs1} is thus (expected) $\Theta(n\log{n})$.
%
  The depth of the tree generated by \texttt{qs1} is isomorphic to the
    depth of a run of the quickselect algorithm, or equivalently to the
    span of a parallel implementation of the quicksort algorithm, both
    of which are known to be (expected) $\Theta(\log{n})$.
%
    By inspection of \texttt{qs2}, we can see that the algorithm takes
    time proportional to the depth of the binary search tree, which is
    $\Theta(\log{n})$. Consider now a random variable for each of the
    $m$ invocations of \texttt{qs2}, each of which takes expected
    $\Theta(\log{n})$ time.  Since the total time is the sum of these
    random variables, and the expectation of the sum is the sum of
    the expectations of the random variables, the bound follows.
\end{proof}

>>>>

\begin{theorem*}
  Consider an execution of \texttt{qs1} with a randomly permuted input
  of $n$ keys and performing $m$ executions of \texttt{qs2} with the
  result of \texttt{qs1}.  The total run-time for this computation is
  $\Theta(n\log{n} + m\log{n})$ in expectation.
\end{theorem*}
\begin{proof}
  We note first that \texttt{qs1} is
  isomorphic to a quicksort algorithm but builds a binary search tree
  instead of combining the returned results in a list.  The run-time
  for \texttt{qs1} is thus (expected) $\Theta(n\log{n})$.
%
  The depth of the tree generated by \texttt{qs1} is isomorphic to the
    depth of a run of the quickselect algorithm, or equivalently to the
    span of a parallel implementation of the quicksort algorithm, both
    of which are known to be (expected) $\Theta(\log{n})$.
%
    By inspection of \texttt{qs2}, we can see that the algorithm takes
    time proportional to the depth of the binary search tree, which is
    $\Theta(\log{n})$. Consider now a random variable for each of the
    $m$ invocations of \texttt{qs2}, each of which takes expected
    $\Theta(\log{n})$ time.  Since the total time is the sum of these
    random variables, and the expectation of the sum is the sum of
    the expectations of the random variables, the bound follows.
\end{proof}
